---
title: "iCenJMH: Efficient Joint Modeling with Longitudinal Data and Interval-Censored Covariates/Outcomes"
output:
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# iCenJMH

`iCenJMH` provides efficient statistical methods for joint modeling of longitudinal and time-to-event data, with a focus on scalable computation using optimized C++ implementations.

---

## Installation

Install the released version from CRAN:

```r
install.packages("iCenJMH")
```

Install the development version from GitHub:

```r
# install.packages("devtools")
devtools::install_github("YOUR_GITHUB_USERNAME/iCenJMH")
```

---

## Basic Usage

```{r}
library(iCenJMH)

# Check OpenMP status
openmp_status()
```

---

## Parallel Computing (OpenMP Support)

This package uses **OpenMP** to accelerate computationally intensive C++ routines.

- On **Linux and Windows**, OpenMP is typically enabled automatically.
- On **macOS**, OpenMP is not enabled by default.
- If OpenMP is unavailable, the package runs in **single-threaded mode**.

---

### Check OpenMP Status

```{r}
openmp_status()
```

- Value > 1 → OpenMP enabled  
- Value = 1 → Serial execution  

---

## macOS Users (Optional Setup)

### Step 1: Install OpenMP runtime

```bash
brew install libomp
```

### Step 2: Configure R

```bash
mkdir -p ~/.R
nano ~/.R/Makevars
```

Add:

```make
CPPFLAGS += -I/opt/homebrew/opt/libomp/include
LDFLAGS += -L/opt/homebrew/opt/libomp/lib -lomp

SHLIB_OPENMP_CFLAGS = -Xclang -fopenmp
SHLIB_OPENMP_CXXFLAGS = -Xclang -fopenmp
```

### Step 3: Reinstall package

```r
install.packages("iCenJMH")
```

### Step 4: Verify

```{r}
openmp_status()
```

---

## Notes

- OpenMP is optional.
- Package works without it.
- Enables faster computation for large datasets.

---
